SETI in the Spatial-Temporal Survey Domain

### 2019-04-25 paper/ms.tex
not much writing Thurs

In Figure \ref{fig:2pt} I show the two-point correlation function for a sample of

trivial example: two point correlation of exoplanets, Figure \ref{fig:2pt}
 not substantively different from field stars, so not a total engineering of the Kepler field. OK however note the selection function of these two populations is not exactly the same, so this can be a tricky metric to  use. considerable effort to ensure well understood sample and biases from non-uniform spatial selection, even in ``simple'' scenarios of galaxy populations in well-studied surveys \citep[e.g.][]{wang2013}. also requires large samples (like with simple spatial overdensities) to determine if something is unusual. This makes it an expensive beacon to create

@@

>>>>

In Figure \ref{fig:2pt} I show the two-point correlation function up to spatial scales of 5 degrees for both the sample of 2,324 transiting exoplanets discovered by the \Kepler primary mission,\footnote{Catalog from \url{http://exoplanetarchive.ipac.caltech.edu}} and for 201,312 stars in the \Kepler field. Since the sample of exoplanets was relatively small, uncertainties shown in Figure \ref{fig:2pt} were estimated by bootstrapping the correlation function 500 times. Here the correlation was done using only the (ra,dec) coordinates for each star or exoplanet system, but can also be done for additional dimensions (e.g. including distance, orbital properties, etc).

%trivial example: two point correlation of exoplanets, Figure \ref{fig:2pt}
 not substantively different from field stars, so not a total engineering of the Kepler field. OK however note the selection function of these two populations is not exactly the same, so this can be a tricky metric to  use. considerable effort to ensure well understood sample and biases from non-uniform spatial selection, even in ``simple'' scenarios of galaxy populations in well-studied surveys \citep[e.g.][]{wang2013}. also requires large samples (like with simple spatial overdensities) to determine if something is unusual. This makes it an expensive beacon to create

@@

This work made use of the gaia-kepler.fun crossmatch database created by Megan Bedell.
